### 2020-05-11 README.Rmd
readme
token
clean other conflicts, added rdaS

devtools::install_github("c1au6i0/covid19census_dev")
```

@@

Demographic metrics and other stats regarding medical conditions and vaccinations were obtained from the [ISTAT](http://dati.istat.it/?lang=en), [Ministero della Salute](http://www.salute.gov.it/portale/home.html). Data regarding `pm2.5` were collected by [Istituto Superiore Per La protexione Ambientale](https://annuario.isprambiente.it/pon/basic/14)

>>>>

devtools::install_github("c1au6i0/covid19census_dev", auth_token = "8ca5cd2bb556a45f1ffeb2e9b44c90d4fbef6cf2")
```

@@

Demographic metrics and other stats regarding medical conditions and vaccinations were obtained from the [ISTAT](http://dati.istat.it/?lang=en), [Ministero della Salute](http://www.salute.gov.it/portale/home.html). Data regarding `pm2.5` were collected by [Istituto Superiore per la Protezione Ambientale](https://annuario.isprambiente.it/pon/basic/14)
